Envelope Estimation using Geometric Properties of a Discrete Real Signal

### 2021-05-07 Papers/01_Pulses_Envelope/00ElsevierPulsesEnvelope.tex
will try to clean bib

Once a radius $ \alpha $ is defined, alpha shapes exhibit the uniqueness property meaning that, for a given set of points and a given radius, only one concave hull exists. When the radius of the circle $ \alpha \to \infty $, concave hulls tend to the convex hulls.

@@

While there is no general formal definition of the envelope of broadband signals \cite{2014Yangnovel,2015Yangtheoretical,2019Jiaempiricalj}, the general intuition is that an envelope is a smooth curve situated as close as possible to the signal \cite{2019Jiaempiricalj}.

@@

Despite its widespread use, and effectiveness in the context of narrowband signals, envelope detection techniques based on the Hilbert transform don't behave well for broadband signals \cite{2012DauSpeech, 2019Jiaempiricalj}, being even physically paradoxical in some cases \cite{1996Loughlinamplitude, 2014Yangnovel}.

@@

Recall from section \ref{mapping} that, before the extraction of the envelope, the original points undergo a change of basis to lie in the Cartesian coordinate system. After the extraction, the inverse operation is performed on the points of the Envelope.

>>>>

Once a radius $ \alpha $ is defined, alpha shapes exhibit the uniqueness property meaning that, for a given set of points and a given radius, only one concave hull exists. When the radius $ \alpha $ of the circle tends to infinity, concave hulls tend to the convex hulls.

@@

While there is no general formal definition of the envelope of broadband signals \cite{2014Yangnovel,2015Yangtheoretical,2019Jiaempirical}, the general intuition is that an envelope is a smooth curve situated as close as possible to the signal \cite{2019Jiaempirical}.

@@

Despite its widespread use, and effectiveness in the context of narrowband signals, envelope detection techniques based on the Hilbert transform don't behave well for broadband signals \cite{2012DauSpeech, 2019Jiaempirical}, being even physically paradoxical in some cases \cite{1996Loughlinamplitude, 2014Yangnovel}.

@@

Recall from section \ref{sec:mapping} that, before the extraction of the envelope, the original points undergo a change of basis to lie in the Cartesian coordinate system. After the extraction, the inverse operation is performed on the points of the Envelope.
